Describing the C-space of asynchronous periodic task using DIT

### 2013-07-22 dit-paper_ieee.tex
Added explanation on DIT to remove redundancy

@@

@@

The first periodic DIT, if it exists, must occur in the transitive period. Indeed, it cannot occur in the incomplete period by definition ($t_d > O_{max}$) and if it occurred in a stationary period, another DIT should have occurred in the transitive period (a contradiction).\\

>>>>

  \label{sct:FPDITexist}

@@

  (Work in Progress...)

@@

The first periodic DIT, if it exists, must occur in the transitive period. Indeed, it cannot occur in the incomplete period by definition ($t_d > O_{max}$) and if it occurred in the $k^{th}$ stationary period, another DIT should have occurred in the transitive period at instant $t_d - k H$ (a contradiction).\\

We show (...) that we can restrict the DBF test to intervals included in the interval $[t_d, t_d + H]$, if the first periodic DIT exists. This will always be a better interval than $[O_{max}, O_{max} + 2H]$ and if the first periodic DIT does not exist (which can be verified as explained in Section \ref{sct:FPDITexist}), the latter interval can be used.\\

To summarize, we reduced the number of equation from every possible interval $[t_1, t_2]$ to only the interval where $t_1$ is an arrival and $t_2$ is a deadline between $[t_d, t_d + H]$ if $t_d$ exists, or between $[O_{max}, O_{max} + 2H]$ otherwise.
